### 2017-05-11 paper/intro.tex
minor tweak

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or inexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.

@@

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization in speeding up testing
in open-source projects.  This is a relevant problem given the
tremendous popularity of open-source development and regression
testing research~\cite{yoo-harman-stvr2012}.  Note that
parallelization is complementary to other approaches to mitigate
testing costs such as (safe) test
selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
integration~\cite{Saff:2003:RWD:951952.952340}.  The dimensions of
analysis we considered in this study are (i) potential, (iii)
adoption, and (iii) flakiness, (iv) speedups.

%% Each dimension
%% focuses on one aspect of the study.

The dimension \textbf{feasibility} measures the potential of
parallelization to reduce testing costs.  In the limit,
parallelization would be fruitless if all projects used short-running
test suites or if the bulk of execution cost was dominated by a single
test in the suite.  The dimension \textbf{adoption} evaluates how
often existing open-source projects use parallelization schemes and
how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance of practicioners to the technology and to understand their
reasons.  The dimension \textbf{issues} reports the observed problems
associated with running tests in parallel.  For example, test
flakiness, which is caused by interference on shared state from
non-deterministic executions of test methods and classes.  Finally,
the dimension \textbf{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  We briefly summarize each of these
dimensions in the following.

@@

\vspace{1ex}\noindent\textbf{Feasibility.}~
We selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven} to assess how prevalent
long-running test suites are.  Section~\ref{sec:eval} details our
methodology to select subjects and to isolate our experiments from
environmental noise.  Results indicate that nearly
\percentMedLongRunning{} of the projects take at least 1m to run their
test suites and \percentLongRunning{} of the projects take at least 5m
to run their suites.  Considering the \numMedLong{} projects in those
two groups, the average execution time is \averageMedLongRunning{}.
Results also show that individual tests are typically short-running,
taking often less than half a second to run.  Furthermore, we found
that only in rare cases few test cases monopolize execution cost
associated with each test suite.  \emph{Overall, our results suggest
  that test suite parallelization has the potential to optimize test
  suites.}

\vspace{1ex}\noindent\textbf{Adoption.}~ We considered two aspects in
measuring technology adoption.  First, we measured usage of
parallelism in open-source projects.  Then, we ran a survey with
developers to understand the reasons that explain resistance to using
the technology.  For the quantitative analysis we checked both
statically (parsing build files) and dynamically (monitoring execution
of build files) for the presence of parallelization.  Considering only
those projects that take longer than a minute to run their test
suites, we found that only \percentParallel{} of them use parallelism.
When correcting this value with the feedback obtained a posteriori
from developers, we realized that the proportion should be higher, of
\percentParallelUpdated{}.  For the qualitative analysis we surveyed
developers from a selection of costly projects that did not use
parallelization.  \emph{Results indicate that test suite
  parallelization is underutilized and dealing with concurrency issues
  related with parallelization (\eg{}, the extra work to organize test
  suite to avoid concurrency errors) was the main barrier for
  adoption.  Other reasons included availability of continuous
  integration services and unfamiliarity with the technology.}

@@

\vspace{1ex}\noindent\textbf{Speedups.}~
%% \Mar{move to here} Intuitively, benefits are
%% proportional to the cost reduction that parallelization brings.  In
%% the limit, however, the overhead of spawning virtual machines or
%% threads can even result in added cost.
\Mar{...revise with scalability results...}
As to avoid introduction of unintended noise when measuring time, we
evaluated effectiveness on projects that we knew a priori ran their
test suite in parallel by default.  Results indicate that the average
speedup of parallelization was \avgSpeedup{}x.  Although we found
cases with very high speedups (\eg{}, 9.2x), we found some cases where
speedups were insignificant.  \emph{Overall, our results suggest that
  it may not be obvious to achieve huge speedups with test suite
  parallelization.}

\Mar{write one or two lessons learned}

>>>>

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or inexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations) is an attractive
solution for running tests.  The proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.

@@

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization to speed up testing
in open-source projects.  This is a relevant problem given the
tremendous popularity of open-source development and regression
testing research~\cite{yoo-harman-stvr2012}.  Note that
parallelization is complementary to other approaches to mitigate
testing costs such as (safe) test
selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
integration~\cite{Saff:2003:RWD:951952.952340}.

The dimensions of analysis we considered in this study are (i)
potential, (iii) adoption, (iv) speedup, and (iii) issues.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practicioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{issues} reports the observed problems associated with running
tests in parallel.  For example, test flakiness, which is caused by
interference on shared state from non-deterministic executions of test
methods and classes.  We briefly summarize our findings in
the following.

@@

\vspace{1ex}\noindent\textbf{Feasibility.}~To assess how prevalent
long-running test suites are we selected \numSubjs{} popular Java
projects from \github{} containing Maven build files~\cite{maven}.
Section~\ref{sec:eval} details our methodology to select subjects and
to isolate our experiments from environmental noise.  Results indicate
that nearly \percentMedLongRunning{} of the projects take at least 1m
to run their test suites and \percentLongRunning{} of the projects
take at least 5m to run their suites.  Considering the \numMedLong{}
projects in those two groups, the average execution time of a test
suite was \averageMedLongRunning{}.  Results also show that test cases
are typically short-running, typically taking less than half a second
to run.  Furthermore, we found that only in rare cases few test cases
monopolize execution cost associated with each test suite.

\vspace{1ex}\noindent\textbf{Adoption.}~ We considered two aspects in
measuring technology adoption.  First, we measured usage of
parallelism in open-source projects.  Then, we ran a survey with
developers to understand the reasons that could explain resistance to
using the technology.\Comment{ For the quantitative analysis we
  checked both statically (parsing build files) and dynamically
  (monitoring execution of build files) for the presence of
  parallelization.}  Considering only those projects that take longer
than a minute to run their test suites, we found that only
\percentParallel{} of them use parallelism.  When correcting this
value with the feedback obtained a posteriori from developers, we
realized that the proportion should be higher, of
\percentParallelUpdated{}.  For the qualitative analysis we surveyed
developers from a selection of costly projects that did not use
parallelization.  Results indicate that test suite parallelization is
underutilized.  Dealing with concurrency-related issues (\eg{}, the
extra work to organize test suite to avoid concurrency errors) and the
availability of continuous integration services were the most
frequently answered reasons for not considering parallelization.

%% \Mar{move to here} Intuitively, benefits are
%% proportional to the cost reduction that parallelization brings.  In
%% the limit, however, the overhead of spawning virtual machines or
%% threads can even result in added cost.

\vspace{1ex}\noindent\textbf{Speedups.}~We used two setups to measure
execution speedups.  In one setup we measured the speedups obtained on
projects that we knew a priori that ran their test suite in parallel
by default.  We did not change parallel configurations on that setup.
For comparison, we disabled parallel execution to obtain the running
time of a sequential execution.  In the other setup, we evaluated how
execution scales with the number of available cores in the machine.
\Mar{need to repeat those!}\Fix{Considering the first setup, results
  indicate that the average speedup of parallelization was
  \avgSpeedup{}x.  Although we found cases with very high speedups
  (\eg{}, 9.2x), we found some cases where speedups were
  insignificant.}

@@

\subsection{Implications}
